\bigskip \noindent{\sc PI Salaries:} We include 3 months salary per year for PI
Becker. Benefits are calculated at the rate of $27.2\%$.  We budget for a $4\%$
annual increase in these salaries.

\bigskip \noindent{\sc Other Salaries:} 1 UW research associate at the
post--doctoral level will be funded at 100\% FTE.  Benefits are calculated at
the rate of $27.2\%$.  We budget for a $4\%$ annual increase in these salaries.

\bigskip \noindent{\sc Equipment:} 1 computer for the UW research associate
(PD1) will be purchased with this grant. We budget for \$4,000 for this machine,
which is an approximate quote for a Pogo Linux Velocity D55 with a dual
quad--core CPU system (computational complexity of PCA scales as approximately
$n^3$) with 24 GB of RAM (the memory requirements of PCA scale as $n^2$) and 8
TB of disk space (primarily to store and back--up the input data, as well as the
derived surfaces).

\bigskip \noindent{\sc Travel:} Due to the distributed nature of this
collaboration, we budget for 3 domestic trips per year for collaboration and
conferences, at the rate of \$1,518 per trip (to cover travel, per diem, and
conference registration).  We budget for 1 international trip per year at the
rate of \$3,014 per trip (to cover travel, per diem, and conference
registration).

\bigskip \noindent{\sc Publication Charges:} Publication costs are budgeted at
the electronic publishing charge of \$115/page, for 30 pages/year.

\bigskip \noindent{\sc Computing Fees:} Computer support fees are budgeted at
the nominal rate of \$67 per person per month for 15 months support (12 months
research associate plus 3 months PI) by the Physics and Astronomy Computing
Services group (PACS) at UW.  We budget for a $3\%$ annual increase in these
costs.

\bigskip \noindent{\sc Other:} Indirect costs for the first year are based on
the MTDC rate of $54.0\%$ per the agreement with DHHS dated 11/30/2010. Indirect
costs for the second and third years are based on the MTDC rate of $54.5\%$ per
the re--negotiated agreement with DHHS dated 9/22/2011.
