\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,setspace,geometry,verbatim,graphicx}
\usepackage{url}
\usepackage{fancybox}

\oddsidemargin  0.05in
\marginparsep 0pt
\topmargin=-0.5in
\textwidth=6.42in
\textheight=9in
%\parskip = 3pt plus 1pt minus 1pt

\begin{document}

\section*{\label{sec:Data-Management-Plan}Data Management Plan}

\setcounter{page}{1}


\subsection*{Project Data Types}

Project outcomes will include publications of algorithmic development, web-based framework for
classification of ongoing surveys, and curricular materials and video lectures (from U.~Washington).
Testing and verification datasets will be collected either from open data programs, or through proprietary access
(with no intention to archive 3rd party primary data).

We will conduct all software development on the publicly available
open-source collaboration website github.com, where many libraries
that serve as the foundation for this project are already hosted.
The website has become a leading collaboration platform;
it enables any internet user to download code and contribute back to the
project, thanks to a powerful peer-review system.
The underlying version control system behind the website is
Git, created to support the development of the Linux kernel. By design,
Git includes ---with every project download--- its entire development
history, ensuring that even if central repositories on github
were to disappear overnight, thousands of cryptographically verifiable,
perfect copies of the project's history exist across the internet.
Hence, there is no point of failure that could cause a loss of
the project's data; it is also possible to switch to a different hosting
system without loss.

Our authoring of educational materials uses tools very similar to
those of software development, and therefore we can use the same infrastructure
described above to make our material publicly available, with all of the
development history intact, and a mechanism to encourage community
participation and further contribution from scientists and educators
outside of our project.


We will, as a safety layer, always host a mirror of all Git repositories
and media files of the project in a central server. This provides an easy to locate, trusted copy of the
active development sites on github (in case of migrating to a new infrastructure, or temporary failure).


\subsection*{Data Standards}

All educational materials will be developed using open standard formats
(\LaTeX{}, HTML, reStructuredText and the openly specified IPython
storage format). This ensures that no proprietary tools are necessary to view,
use, or contribute back, to any of the project outcomes.


\subsection*{Privacy and Intellectual Property Issues}

Our project does not need collection of personally sensitive data; we can
thus make all of our outcomes available under open source licensing
terms without any requirements of confidentiality.


\subsection*{Re-Use and Re-Distribution Licensing Terms}

All outcomes will be made available to the public following the principles
set forth in the Reproducible Research Standard proposed by Stodden
\cite{Stodden-09}:
\begin{itemize}
\item All code we develop for this project will be made available under
the terms of the open source BSD license,%
\footnote{\url{http://www.opensource.org/licenses/bsd-license.php}%
} whenever possible (i.e., as long as it is completely original code
or derived from similarly licensed code). In the event that we contribute
to projects with existing licenses that are not compatible with the
BSD license, such as LGPL- or GPL-licensed projects, we will contribute
to these projects under the terms of their own licenses.
\item Educational materials, documentation and other media (such as online
videos) will be released under the terms of the Creative Commons Attribution
License CC~BY,%
\footnote{\url{http://creativecommons.org/licenses/by/3.0}%
} except in cases where we may reuse materials released under a more
restrictive license such as the Attribution-ShareAlike CC~BY-SA%
\footnote{\url{http://creativecommons.org/licenses/by-sa/3.0}%
} (used by e.g. Wikipedia). Such materials would be released under
the terms of the original license, in compliance with its original
terms.
\item Since US Copyright law prevents the copyright of raw facts, any data
generated as part of our project will be released under the Creative
Commons CC0 terms,%
\footnote{\url{http://creativecommons.org/about/cc0}%
} i.e., fully released to the public domain without further copyright
claims.
\end{itemize}

\subsection*{Long-Term Archival Plans}

While YouTube is likely to outlast the length of our funding, and Git's
distributed nature effectively uses the entire internet as a backup
system, as indicated above we will use our server to host a mirror
of all of our materials on the UC Berkeley network.

\begin{thebibliography}{99}

\bibitem{Stodden-09}
Stodden, V. (2009).
\newblock {Enabling Reproducible Research: Open Licensing For Scientific Innovation}.
\newblock {\textit{International Journal of Communications Law and Policy}, vol. 13}.

\end{thebibliography}




\end{document} 