\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,setspace,geometry,verbatim,graphicx}
\usepackage{url} \usepackage{fancybox}

\oddsidemargin  0.05in \marginparsep 0pt \topmargin=-0.5in \textwidth=6.42in
\textheight=9in %\parskip = 3pt plus 1pt minus 1pt

\begin{document}

\section*{Mentoring Plan}

\setcounter{page}{1}

\subsection*{Postdoc Mentoring Plan}

We plan a comprehensive mentoring program for the postdoctoral scholars
associated with this project. The most robust mentoring starts before the
scholar arrives: by clearly articulating the project goals in the job position
advertisement, the expectations of the postdoc who eventually accepts the
position will be explicit. These expectations---as well as the expectations of
those senior personnel in mentoring positions---will be reviewed with the
scholar upon arrival. An individual development plan (IDP), a planning process
that identifies both professional development needs and career objectives, will
be prepared. The IDP includes any suggestions on graduate courses that might
help the postdoc to actively participate in the cross-disciplinary
project\footnote{The University of California \textit{Academic Personnel Policy}
provides explicit expectations for mentors of postdoctoral scholars which we
will abide by: ``Faculty mentors are responsible for guiding and monitoring the
advanced training of Postdoctoral Scholars. In that role, faculty mentors should
make clear the goals, objectives, and expectations of the training program and
the responsibilities of Postdoctoral Scholars. They should regularly and
frequently communicate with Postdoctoral Scholars, provide regular and timely
assessments of the Postdoctoral Scholar's performance, and provide career advice
and job placement assistance.'' (390-6 -- Responsibility). There are similar
expectations at U. Washington.}.

\begin{itemize}

\item \textbf{From the Outset:} The PI and co-PIs will 1) explicitly discuss the
scientific and technical expectations of the postdocs and insure those are in
sync with our expectations, 2) discuss the roles in the mentor/mentoree
relationship, 3) identify key resources at each institution for assistance in
professional development (e.g. the Office of Post--doctoral Affairs at U.
Washington), 4) inform the postdocs of avenues for conflict resolution
(following the respective guidelines and program offices at each institution),
and 5) discuss a timeline for progress on the project.

\item \textbf{Mentoring a Mentor:} The postdocs will be encouraged to take an
active role in co--mentoring (along with the PI and co--PIs) within the graduate
departments of each institution.  This plays a dual role in providing valuable,
early mentoring experiences in academia for the postdoc while creating an
additional resource for mentored students as they progress through their own
research. We will conduct periodic conversations about graduate student
mentoring to help the postdocs reinforce positive results and address
difficulties.

\item \textbf{Formal Reviews:} Every 6 months the PI and co--PIs will provide a
formal review to access the research progress, strengths, and areas needing
improvement.

\item \textbf{Career Laddering:} The PI and co-PIs will informally (but
regularly) address career plans and job search strategies with the postdocs,
help them network at conferences both domestic and international, obtain
invitations to speak at other universities on the subject of this proposal, and
work on grant and job applications.

\item \textbf{Encouragement:} Critical to the success of the postdoc (and this
project) will be their continual encouragement to strive for excellence in their
research, allowing ample room for creativity and independence.  To this end we
will provide for an 80/20 split in the amount of time the postdocs are expected
to work on this proposal vs. allowed to work on additional scientific pursuits.

\end{itemize}

\end{document}